Efficient Coalition Formation \\ for Web Services

### 2013-06-22 papers/coalition-journal-extension/coalition_journal.tex
Added new charts

\subsection{Taxtation and Community Stability}\label{s:tax}

@@

>>>>

\subsection{Taxtation, Subsiding and Community Stability}\label{s:tax}

@@

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{taxtation.eps}
\caption{Analysis of community subsiding coefficient $\lambda$ on average community size (a), cost (b), number of tasks performed (c), and average quality of service of tasks performed (d).} \label{f_taxtation}
\end{figure}

texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext

\begin{figure*}[!t]
\centerline{\includegraphics[width=6.75in]{tax_dyn.eps}}
\caption{Analysis of community subsiding coefficient $\lambda$ having web service different stability levels of $\tau$ on average community size, number of tasks performed, and average quality of service, and average cost/income of communities.}
\label{fig_dynamic_taxtation}
\end{figure*}

texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{avg_task_ws_done.eps}
\includegraphics[width=3in]{avg_qos_ws_done.eps}
\includegraphics[width=3in]{avg_avail_ws_done.eps}
\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
\end{figure}

texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
